Flatiron cleaning

### 2021-12-15 Rmd/rdi analysis.Rmd
Start imputation

           "histology", "stagecat",

@@

           "bmi_at_dx", bmi_cat, "BSA",
           "stagecat")) %>% 
  tbl_summary(by = raceeth) %>% bold_labels() %>% add_overall() %>% add_p() %>% bold_p(t = .05)
```
<br>

@@

           "bmi_at_dx", bmi_cat, "BSA",
           "stagecat")) %>% 
  tbl_summary(by = bmi_cat) %>% bold_labels() %>% add_overall() %>% add_p() %>% bold_p(t = .05)
```
<br>

@@

@@

@@

@@

@@

@@

@@

<span style="color:green">**Table 4 Summary treatment data by race**</span>
```{r Table 4}
# tbl1 <- 
  Frontline %>% distinct(patientid, .keep_all = TRUE) %>% 
  select(c(raceeth,
           "debulking", "therapy"
           )) %>% 
  mutate(debulking = factor(debulking, levels = c("Suboptimal", "Optimal"))) %>% 
  tbl_summary(by = raceeth) %>% bold_labels() %>% add_overall() %>% add_p() %>% bold_p(t = .05)
```
<br>

@@

```{r echo=FALSE, out.width='50%'}
knitr::include_graphics('/Users/colinccm/Documents/GitHub/Peres/lab_logo/Peres hex.png')
```

>>>>

           "histology", imp_histology, "stagecat", imp_stagecat,

@@

           "bmi_at_dx", bmi_cat, "BSA",
           "stagecat", imp_stagecat)) %>% 
  tbl_summary(by = raceeth) %>% bold_labels() %>% add_overall() %>% add_p() %>% bold_p(t = .05)
```
<br>

@@

           "bmi_at_dx", bmi_cat, "BSA",
           "stagecat", imp_stagecat)) %>% 
  tbl_summary(by = bmi_cat) %>% bold_labels() %>% add_overall() %>% add_p() %>% bold_p(t = .05)
```
<br>

@@

Frontline %>% 
  distinct(patientid, .keep_all = TRUE) %>% 
  ggplot(aes(x= imp_histology))+
  geom_bar()+
  theme_minimal(base_size = 14)+
  labs(title = "Histology")+
  coord_flip()

@@

Frontline %>% 
  distinct(patientid, .keep_all = TRUE) %>% 
  ggplot(aes(x= imp_stagecat))+
  geom_bar()+
  theme_minimal(base_size = 14)+
  labs(title = "Stage")+
  coord_flip()

@@

Frontline %>% 
  distinct(patientid, .keep_all = TRUE) %>% 
  ggplot(aes(x= raceeth, fill = imp_histology))+
  geom_bar(position = "fill")+
  theme_minimal(base_size = 14)+
  labs(title = "Histology")+
  coord_flip()

@@

Frontline %>% 
  distinct(patientid, .keep_all = TRUE) %>% 
  ggplot(aes(x= raceeth, fill = imp_stagecat))+
  geom_bar(position = "fill")+
  theme_minimal(base_size = 14)+
  labs(title = "Stage")+
  coord_flip()

@@

ggsurvplot(survfit(Surv(month_at_os, vitalstatus) ~ imp_stagecat, data=Frontline %>% 
                     distinct(patientid, .keep_all = TRUE)),
           title = "OS from date of diagnosis", 
           font.main = c(24, "bold", "black"), 
           font.x = c(20, "bold", "black"), font.y = c(20, "bold", "black"), 
           font.legend = c(14, "bold", "black"), font.tickslab = c(18, "bold", "black"), 
           size = 1.5,

@@

ggsurvplot(survfit(Surv(month_at_os_from_treatment, vitalstatus) ~ imp_stagecat, data=Frontline %>% 
                     distinct(patientid, .keep_all = TRUE)),
           title = "OS from date of first treatment", 
           font.main = c(24, "bold", "black"), 
           font.x = c(20, "bold", "black"), font.y = c(20, "bold", "black"), 
           font.legend = c(14, "bold", "black"), font.tickslab = c(18, "bold", "black"), 
           size = 1.5,

@@

<span style="color:green">**Table 4 Summary treatment data by race**</span>
```{r Table 4}
# tbl1 <- 
  Frontline %>% distinct(patientid, .keep_all = TRUE) %>% 
  select(c(raceeth,
           "debulking", imp_debulking , "therapy"
           )) %>% 
  mutate(debulking = factor(debulking, levels = c("Suboptimal", "Optimal"))) %>% 
  tbl_summary(by = raceeth) %>% bold_labels() %>% add_overall() %>% add_p() %>% bold_p(t = .05)
```
<br>

@@

```{r echo=FALSE, out.width='30%'}
# knitr::include_graphics('/Users/colinccm/Documents/GitHub/Peres/lab_logo/Peres hex.png')
```
